Build Your Own EV: A Rapid Energy-Aware Synthesis of Electric Vehicles

### 2018-07-30 draft/draft.tex
Update current version

We demonstrate how the electric vehicle powertrain setup impacts on the energy consumption and the resultant driving range with a campus mail delivery example. Fig.~\ref{fig:example_route}(a) shows the campus mail delivery route example. There are total eight mail drops in the route, and the campus speed limit is 20 mph. The road slope of the route varies from -5.6\% to 8.5\%, which is extracted from Google Earth as shown in Fig.~\ref{fig:example_route}(b). We extract a reference speed profile for the mail delivery driving cycle also in Fig.~\ref{fig:example_route}(b).

>>>>

%We demonstrate how the electric vehicle powertrain setup impacts on the energy consumption and the resultant driving range with a campus mail delivery example. Fig.~\ref{fig:example_route}(a) shows the campus mail delivery route example. 
%There are total eight mail drops in the route, and the campus speed limit is 20 mph. The road slope of the route varies from -5.6\% to 8.5\%, which is extracted from Google Earth as shown in Fig.~\ref{fig:example_route}(b). We extract a reference speed profile for the mail delivery driving cycle also in Fig.~\ref{fig:example_route}(b).
%
\textcolor{red}{We demonstrate how the electric vehicle powertrain setup impacts on the energy consumption and the resultant driving range with a campus mail delivery example as shown in Fig.~\ref{fig:example_route}(a). 
There are total eight mail drops in the route, and the campus speed limit is 20 mph. The road slope of the route varies from -5.6\% to 8.5\%, and the driving cycle is determined by the mail drop locations and the speed limit as shown in Fig.~\ref{fig:example_route}(b).}
